Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-07 Response/response-4.tex

\cmnts{n} - \textit{p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}

\resp To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point. Since the operating point happens to be the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set. Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective. It is explained in detail in Appendix B on the convergence analysis of the centralized algorithm.

\cmnts{o} - \textit{p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?}

\resp We thank the reviewer for the critical comment. It is true that the convex problem does not need to have a unique solution in general. By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function. The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20). Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b). When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain unique set of transmit precoders. On contrary, it has multiple solutions when the objective is zero even for a single BS. In this case, we can use a regularization term with the total power in the objective to obtain an unique solution. We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C. It makes the objective strictly convex, therefore, it has a unique minimum.

### 2015-03-07 Report/convergence_centralized.tex
halfoocked

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{m}}
\newcommand{\my}{\mbf{w}}
\newcommand{\mz}{\mbfa{\gamma}}
\newcommand{\mxb}{{{\mbf{m}}}}
\newcommand{\myb}{{{\mbf{w}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}

To prove the convergence of the transmit precoders, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be coercive and bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be monotonically decreasing in each iteration
	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
\end{itemize}
Using \cite[Prop. A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied. Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.

Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using \cite[Th. 3.14]{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a limiting point. The one-to-one mapping between the feasible domain and the objective function value is required to prove the convergence of the transmit and the receive beamformers upon convergence of the objective function value iterates. Note that the iterative relaxed convex subproblems has the unique solution but not the original nonconvex problem. Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary matrix rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different phase rotations. The limiting point of the iterative algorithm is susceptible to the initial feasible point, since it is the operating point for linearizing the nonconvex \ac{DC} constraint.

\subsection{Boundedness and Compactness}

The feasible set of the relaxed nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded due to the total power constraint on the transmit precoders \eqref{eqn-6.4}. Note that the other variables are also bounded in accordance with this constraint. Since the feasible set also includes the boundary value due to the inequality constraint, it is closed and compact.

To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective. Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below. Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive. Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_infty}. Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} correspond to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} = \{ \; \mx,\my,\mz \; \big | \; & h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
								& g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \; \} \nonumber
\end{IEEEeqnarray}

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}. We adopt \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}. Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration. For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.

To begin with, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
\begin{multline} \label{con-relax}
\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
\end{multline}
Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
\begin{subeqnarray} \label{con-m}
	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
\end{subeqnarray}
Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us consider that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution for the \me{\ith{k}} iteration. Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
\allowdisplaybreaks{\begin{multline}\label{con-sub-set}
h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
\end{multline}}
Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}. At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective function \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
\begin{multline} \label{con-convergence}
f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}). 
\end{multline}
Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}. Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point for \eqref{con}, since it is the minimizer only over the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.

@@

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\allowdisplaybreaks{\begin{multline}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{multline}}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective value sequence as
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
\end{equation*}
The feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration. Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.

@@

To prove the convergence of the transmit and the receive beamformers, we use the uniqueness in the mapping between the transmit and receive beamformers with respect to the objective function. The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, is achieved due to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}. The linearized \eqref{eqn-8} can be written as
\begin{multline} \label{uniqueness-1}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for \ac{MSE} expression as
\begin{multline} \label{uniqueness-2}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is unique for the given set of transmit precoders. It is due to the constraints \eqref{uniqueness-1} and \eqref{uniqueness-2}, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.

When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}. To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can follow the regularization approach discussed in Appendix \ref{a-3} without affecting the optimal solution.
%we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
%\begin{equation*}
%\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
%\end{equation*}
%for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.

>>>>

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{m}}
\newcommand{\my}{\mbf{w}}
\newcommand{\mz}{\mbfa{\gamma}}
\newcommand{\mxb}{{{\mbf{m}}}}
\newcommand{\myb}{{{\mbf{w}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
\newcommand{\ma}{\mbf{x}}

To prove the convergence of the transmit precoders, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be coercive and bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
Using \cite[Prop. A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied. Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.

\subsection{Boundedness of the Objective and Compactness of the Set}

The feasible set of the problem \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.

The minimum value of the norm operator in the objective is zero, \textit{i.e}, the limiting point is \me{< -\infty}, therefore it is bounded below. The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive. Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_infty}. Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2,f} are convex and \me{h} is a linear function. Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both. The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}. Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} = \{ \; \mx,\my,\mz \; \big | \; & h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
								& g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \; \} \nonumber
\end{IEEEeqnarray}

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}. We adopt \ac{SCA} presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}. Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration. Let \me{\iter{\mz}{\ast|y}{i}} be the optimal value of \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.

To begin with, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
\begin{multline} \label{con-relax}
\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
\end{multline}
Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
\begin{subeqnarray} \label{con-m}
	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
\end{subeqnarray}
Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us consider that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution for the \me{\ith{k}} iteration. Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
\allowdisplaybreaks{\begin{multline}\label{con-sub-set}
h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
\end{multline}}
Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}. At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
\begin{multline} \label{con-convergence}
f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}). 
\end{multline}
Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}. Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of \eqref{con}, since it is the minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.

@@

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\allowdisplaybreaks{\begin{multline}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{multline}}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective value sequence as
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
\end{equation*}
The \ac{AO} update follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. %Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.

@@

The uniqueness of the transmit precoders and the receive beamformers for the convex subproblem can be guaranteed in general by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}. Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.

When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems. To obtain an unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
%we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
%\begin{equation*}
%\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
%\end{equation*}
%for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.

\subsection{Convergence of the beamformer iterates}

Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and let \me{\mc{A}} be a point-to-set mapping from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}. The objective function \me{f} in \eqref{con-cvx} is continuous and the iterative algorithm yields monotonically decreasing objective values \me{f(\ma^{(n)}) \leq f(\ma^{(n-1)})} in each iteration. Therefore, the operator \me{\mc{A}} is monotonic with respect to a continuous objective function \me{f} yielding a sequence of beamforming iterates \me{\{\ma^{(n)}\}}. The following conditions are satisfied by the iterative algorithm \cite{meyer1976sufficient}.
\begin{itemize}

\end{itemize}

. Let \me{\{\ma^{(n)}\}} be the sequence of beamforming iterates generated by the function \me{f} in \eqref{con-cvx} and the mapping operator \me{\mc{A}}. To prove the convergence of the beamformer iterates, following conditions are required \cite{meyer1976sufficient}.
\begin{itemize}
\item[(e)] The mapping operator \
\end{itemize}

approaches a limiting or accumulation point \me{\ma^{\ast} \in \mc{F}^\ast} as \me{n \rightarrow \infty}, where \me{\mc{F}^{\ast}} represents the set of accumulation points for the
